### 2014-11-09 Abstract.tex
stuff

We present a new framework for modular verification of hardware designs in the
style of the Bluespec language.  That is, we formalize the idea of components
in a hardware design, with well-defined input and output channels; and we show
how to specify and verify components individually, with machine-checked proofs
in the Coq proof assistant.  As a demonstration, we verify a fairly realistic
implementation of a multicore shared-memory system consisting of two types of
components:  memory-system and processor.  Both components include nontrivial
optimizations, with the memory system employing an arbitrary hierarchy of cache
nodes that communicate with each other concurrently, and with the processor
doing speculative execution of many concurrent read operations.  Nonetheless,
we prove that the combined system implements sequential consistency.  One
interesting aspect of the proof is that the memory component is well-specified
to be reusable for systems implementing a variety of weak memory models.  To
our knowledge, our memory-system system proof is the first machine verification
of a cache-coherence protocol parameterized over an arbitrary cache hierarchy,
and our full-system proof is the first machine verification of sequential
consistency for a multicore hardware design that includes caches and
speculative processors.

>>>>

We present a new framework for modular verification of hardware designs in the
style of the Bluespec language.  That is, we formalize the idea of components
in a hardware design, with well-defined input and output channels; and we show
how to specify and verify components individually, with machine-checked proofs
in the Coq proof assistant.  As a demonstration, we verify a fairly realistic
implementation of a multicore shared-memory system with two types of
components:  memory-system and processor.  Both components include nontrivial
optimizations, with the memory system employing an arbitrary hierarchy of cache
nodes that communicate with each other concurrently, and with the processor
doing speculative execution of many concurrent read operations.  Nonetheless,
we prove that the combined system implements sequential consistency.  One
interesting aspect of the proof is that the memory component is well-specified
to be reusable for systems implementing a variety of weak memory models.  To
our knowledge, our memory-system system proof is the first machine verification
of a cache-coherence protocol parameterized over an arbitrary cache hierarchy,
and our full-system proof is the first machine verification of sequential
consistency for a multicore hardware design that includes caches and
speculative processors.

### 2014-11-09 Introduction.tex
stuff

LTSes as hardware descriptions are an established
idea~\cite{HoeArvind:TRSSynthesis1, Hoe:TCAD}, and there are compilers that
convert LTSes into efficient hardware.  Our work is based on the Bluespec
language~\cite{BSV:LangRef, Bluespec:TFRG}, which served as the model for the
formalism of this paper.  Bluespec models hardware components as atomic rules
of a transition system over state elements, and there is a commercial compiler
to synthesize such codes into register transfer-level circuits (i.e., Verilog code) with
competitive performance.  Our cache-coherent memory system is directly
transliterated from a Bluespec
implementation~\cite{DNA:CoherenceImplementation} used to implement a
cycle-accurate simulator for a multi-processor PowerPC system~\cite{Khan:PowerPc}. The hardware synthesized
from that implementation is rather efficient: an 8-core system with a 2-level
cache hierarchy can run 55 million instructions per second on the BEE FPGA
board\cite{bee2}. Figure \ref{both} gives an example of an LTS inference rule
transliterated directly from an actual Bluespec rule used in the PowerPC
system. In Bluespec notation, only those state elements whose value changes are
mentioned on the RHS of a rule; in
contrast LTSes employ a more functional notation. (The meaning of this rule
will become clear in Section \ref{sec:caches})

The main contributions of this paper are:

\begin{itemize} 
\item Identification of an interface between the processor and the memory
components of a multi-processor system that enables modular implementation and
verification.

>>>>

LTSes as hardware descriptions are an established
idea \cite{HoeArvind:TRSSynthesis1, Hoe:TCAD}, and there are compilers that
convert LTSes into efficient hardware.  Our work is based on the Bluespec
language \cite{BSV:LangRef, Bluespec:TFRG}, which served as the model for the
formalism of this paper.  Bluespec models hardware components as atomic rules
of a transition system over state elements, and there is a commercial compiler
to synthesize such codes into register transfer-level circuits (i.e., Verilog code) with
competitive performance.  Our cache-coherent memory system is directly
transliterated from a Bluespec
implementation \cite{DNA:CoherenceImplementation} used to implement a
cycle-accurate simulator for a multi-processor PowerPC system \cite{Khan:PowerPc}. The hardware synthesized
from that implementation is rather efficient: an 8-core system with a 2-level
cache hierarchy can run 55 million instructions per second on the BEE FPGA
board \cite{bee2}. Figure \ref{both} gives an example of an LTS inference rule
transliterated directly from an actual Bluespec rule used in the PowerPC
system; its meaning will become clear in Section \ref{sec:cc}. In Bluespec
notation, only those state elements whose values change are mentioned in the
rule; in contrast LTSes employ a more functional notation.

The main contributions of this paper are:
\vspace{-.3cm}
\begin{itemize} 
\item Identification of an interface between the processor and the memory
components of a multi-processor system that enables modular implementation and
verification.
